Supplement for Open-Source machine learning BANTER acoustic classification of beaked whale echolocation pulses

### 2023-08-28 hawaii/beakerBanter_hawaii.Rmd
Revise Hawaii and Manuscript
Revise Hawaii to reduce HeatPlot to show top 10; revise manuscript based on Cory's comments, update supplement.

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/hawaii_ec_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap")
dev.off()
ec_hawaii_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap")

png(('../manuscript/manuscript_files/hawaii_ici_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap")
dev.off()
ici_hawaii_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap")
```

>>>>

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/hawaii_ec_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)
dev.off()
ec_hawaii_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/hawaii_ici_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)
dev.off()
ici_hawaii_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)
```

### 2023-08-28 manuscript/Supplement.qmd
Revise Hawaii and Manuscript
Revise Hawaii to reduce HeatPlot to show top 10; revise manuscript based on Cory's comments, update supplement.

---
title: Supplement for Open-Source machine learning BANTER acoustic classification of a cryptic echolocating species
author: Shannon Rankin
date: last-modified
output: pdf
---

@@

# NAtlantic
## EC Model

Detector Model:  ntree=1e4, sampsize=3; 
Event Model: ntree=1e4, sampsize=3
```{r,  NAtlantic EC Model Figure, echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=5; 
Event Model: ntree=1e4, sampsize=5
```{r, NAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

natlantic_alt_Figure <-image_append(c(prox, heat, vote))
natlantic_alt_Figure<- image_append(c(confuse, natlantic_alt_Figure), stack=TRUE)
print(natlantic_alt_Figure, info=FALSE)
```

# SAtlantic
## EC Model
Detector Model:  ntree=1e4, sampsize=2; 
Event Model: ntree=1e5, sampsize=1
```{r, SAtlantic EC Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=4; 
Event Model: ntree=1e5, sampsize=2
```{r, SAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# Hawaii
## EC_ICI Model
Detector Model:  ntree=5e3, sampsize=5; 
Event Model: ntree=1e4, sampsize=4
```{r, Hawaii EC_ICI Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# EPacific
## EC Model
Detector Model:  ntree=1e4, sampsize=3; 
Event Model: ntree=1e4, sampsize=4

```{r, EPacific EC Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

>>>>

---
title: Supplement for Open-Source machine learning BANTER acoustic classification of beaked whale echolocation pulses
author: Shannon Rankin
date: last-modified
output: pdf
---

@@

# NAtlantic
Results for the NAtlantic EC (only) model are provided in @fig-natlantic_EC (Detector Model: *sampsize* = 3, *ntree* = 10,000; Event Model: *sampsize* = 3, *ntree* = 10,000).

```{r,  NAtlantic EC Model Figure, echo=FALSE}
#| label: fig-natlantic_EC
#| fig-cap: BANTER classification results from the NAtlantic dataset including echolocation pulses (EC). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# SAtlantic

Results for the SAtlantic EC (only) model are provided in @fig-satlantic_EC (Detector Model: *sampsize* = 8, *ntree* = 10,000; Event Model: *sampsize* = 1, *ntree* = 100,000).

```{r, SAtlantic EC Model Figure,  echo=FALSE}
#| label: fig-satlantic_EC
#| fig-cap: BANTER classification results from the SAtlantic dataset including echolocation pulses (EC). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

Results for the SAtlantic EC_IPI_ALT model are provided in @fig-satlantic_EC_IPI_ALT (Detector Model: *sampsize* = 4, *ntree* = 10,000; Event Model: *sampsize* = 3, *ntree* = 100,000).

```{r, SAtlantic EC_IPI_ALT Model Figure,  echo=FALSE}
#| label: fig-satlantic_EC_IPI_ALT
#| fig-cap: BANTER classification results from the alternative SAtlantic dataset including echolocation pulses and inter-pulse interval with a large sampsize (EC_IPI_ALT). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# Hawaii

Results for the Hawaii EC_IPI model are provided in @fig-hawaii_EC_IPI (Detector Model: *sampsize* = 5, *ntree* = 100,000; Event Model: *sampsize* = 4, *ntree* = 10,000).

```{r, Hawaii EC_IPI Model Figure,  echo=FALSE}
#| label: fig-hawaii_EC_IPI
#| fig-cap: BANTER classification results from the Hawaii dataset including echolocation pulses and inter-pulse interval (EC_IPI). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# EPacific

Results for the EPacific EC (only) model are provided in @fig-epacific_EC (Detector Model: *sampsize* = 4, *ntree* = 10,000; Event Model: *sampsize* = 4, *ntree* = 10,000).

```{r, EPacific EC Model Figure,  echo=FALSE}
#| label: fig-epacific_EC
#| fig-cap: BANTER classification results from the EPacific dataset including echolocation pulses (EC). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

Results for the EPacific EC (only) model are provided in @fig-epacific_EC_IPI (Detector Model: *sampsize* = 3, *ntree* = 10,000; Event Model: *sampsize* = 4, *ntree* = 10,000).

```{r, EPacific EC IPI Model Figure,  echo=FALSE}
#| label: fig-epacific_EC_IPI
#| fig-cap: BANTER classification results from the EPacific dataset including echolocation pulses and inter-pulse interval (EC_IPI). Confusion matrix (a) provides the percent correct classification for each species (pct.correct), lower confidence intervals (LCI_0.95), upper confidence intervals (UCI_0.95), and priors (expected error rate). Proximity plot (b) for species events from BANTER model (central dot color represents true species identity; color of circle surrounding dot represents BANTER species classification). Heat map (c) for ranks of ten most important variables; colors scale from most important predictors (dark red) to least important predictors (dark blue). Vote Plot (d) shows the vote distribution for each event (vertical slice) for each species; distribution of votes by species is shown by their representative color.
#| #| fig-width: 10
#| fig-height: 10
#| fig-align: center
#| out-width: 100%
#| echo: false
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

epacific_ici_Figure <-image_append(c(prox, heat, vote))
epacific_ici_Figure<- image_append(c(confuse, epacific_ici_Figure), stack=TRUE)
print(epacific_ici_Figure, info=FALSE)
```
